---
# The book's home page. Edit the title/subtitle/description to introduce
# yourself and what this portfolio contains.
title: "My Data Science Portfolio"
author: "Your Name"
date: today
---

```{r}
#| include: false
# Package setup lives in one shared chunk so every chapter starts from a
# consistent environment. Add libraries you use across the book here.
library(tidyverse)
```

## Welcome 👋

This is **your** data science portfolio. Over the semester it will grow from a
single exploratory data analysis (EDA) project into a collection of
reproducible analyses, each versioned with git, with dependencies pinned via
renv/uv, and published to a URL on Posit Connect.

The chapters in this book are:

- **Chapter 1, EDA project**: your first real analysis, sourcing a dataset
  you care about by code from an open-data portal (data.gouv.fr, or your own
  country's) and (optionally) pinning it with `{pins}`.
- **Chapters 2 & 3, later courses**: placeholders that other instructors will
  fill in over the semester. Leave them in place.

## How to use this scaffold

This folder is a *starter book*: copy it into your own workspace and make it
yours. See [`README.md`](README.md) for the full walkthrough.

```{r}
#| label: fig-eda-sneak-peek
#| fig-cap: "A first glimpse of your data. Replace this figure with your EDA output."
# A tiny placeholder plot so the book renders before you add your own analysis.
ggplot(data.frame(x = rnorm(200), y = rnorm(200)), aes(x, y)) +
  geom_point(alpha = 0.4, colour = "#2E7D6B") +
  labs(x = "your variable", y = "your other variable")
```

The book is **language-agnostic**: Chapter 1 uses R, but later chapters could
just as easily use Python. What makes it reproducible is the pipeline around
it: data sourced reproducibly, code that renders from source, dependencies
pinned, everything under version control.
