---
title: "Chapter 1 · My EDA project"
author: "Your Name"
date: today
---

> **How to fill this chapter in**
> This is your main portfolio piece. The numbered sections below follow the
> **IMRAD** structure of research: question ≈ *introduction*, getting the
> data + cleaning decisions ≈ *methods*, plotting the story ≈ *results*, and
> findings ≈ *discussion*. In the *Reproducible Workflows* course:
>
> - **Session 2** lab: find a dataset you care about on an open-data portal
>   (data.gouv.fr or your own country's), source it **reproducibly by code**,
>   run an EDA, clean the data, and commit it to git.
> - **Session 3** work block: finish and polish the chapter, pin your data and
>   environment, open a pull request for review, and publish the book to a URL.
>
> Everything between the `TODO` markers below is a template to replace with
> your own content.

## The question

<!-- TODO: In a sentence or two, what question are you trying to answer with this dataset?  -->

## Getting the data

The data is sourced **by code** from an open-data portal of your choice. Because
the download lives inside the document, it is recorded in the analysis itself;
anyone who re-renders this document gets the same data and the same results.
Record the dataset's **publisher and URL** in the text so the provenance is
explicit.

The only portal-specific part is the *fetch*. This template shows two ways;
use the one that fits your portal:

- **`{rdatagouv}`** (data.gouv.fr only, optional): search/download from R.
- **Any portal by URL**: `download.file()` works with any portal's direct
  download link.

```{r}
#| label: setup
#| message: false
# Load what you use. {rdatagouv} only if you're on data.gouv.fr and want it.
# library(rdatagouv)    # search / download datasets from data.gouv.fr
library(janitor)        # clean column names, tabulate with tabyl()
library(naniar)         # visualise missing values
library(skimr)          # one-line data summary with skim()
```

```{r}
#| label: download
#| message: false
# TODO: replace with the code you wrote in the Session-2 lab.
# Option A — data.gouv.fr via {rdatagouv}:
# ds <- get_dataset("my-dataset-slug"); url <- ds$resources$url[1]
# Option B — any portal by direct URL:
# url <- "https://www.example-portal.org/.../my-data.csv"
# download.file(url, "data/my-data.csv")
```

> **Optionally pin the fetched copy** with `{pins}` so the chapter reads from a
> versioned local board instead of hitting the network on every render:
>
> ```r
> board <- pins::board_folder("pins/", versioned = TRUE)
> pins::pin_write(board, dat, "my-data", type = "csv")
> dat    <- pins::pin_read(board, "my-data")
> ```


## A first look

```{r}
#| label: skim
#| fig-cap: "A one-line summary of the dataset."
# The skim() output gives you type, missingness and distributions at a glance.
# skim(dat)
```

```{r}
#| label: missingness
#| fig-cap: "Missing values across variables."
# vis_miss(dat) — where is data missing, and why might that be?
```

## Cleaning decisions {#sec-cleaning}

<!-- TODO: document the decisions you made while cleaning the data. What did you
rename, recode, or drop, and why? A defensible cleaning decision is a feature
of a good analysis, not an afterthought. -->

## Plotting the story

<!-- TODO: replace with your figures. Give every figure a caption and refer to
it in the text (e.g. "Fig. 1 shows that …"). If a figure uses randomness
(sampling, jitter, a simulation), fix the seed *inside* that cell with
`withr::with_seed(2025, { ... })` so the figure is identical on every render. -->

```{r}
#| label: fig-main
#| fig-cap: "The central figure of your analysis."
```

## Findings

<!-- TODO: what did you learn? This is your discussion: put your findings and
the original question back into perspective. Keep it honest: say what you
found, and what you did NOT find. -->

---

*This chapter is your semester's centrepiece. Revisit it as you learn new
techniques and make it your best work by the final gallery walk.*
