---
title: "Chapter 1 · My EDA project"
author: "Yi Qian"
format: html
date: today
---


## The question

What is the dominant factor to effect the potential of photovoltaic power generation?


## Getting the data

The data is sourced **by code** from an open-data portal of your choice. Because
the download lives inside the document, it is recorded in the analysis itself;
anyone who re-renders this document gets the same data and the same results.
Record the dataset's **publisher and URL** in the text so the provenance is
explicit.

The only portal-specific part is the *fetch*. This template shows two ways;
use the one that fits your portal:

- **`{rdatagouv}`** (data.gouv.fr only, optional): search/download from R.
- **Any portal by URL**: `download.file()` works with any portal's direct
  download link.

```{r}
#| label: setup
#| message: false


pak::pak("nbafrank/uvr-r")   # the uvr R package, from GitHub
uvr::install_uvr()           # installs the uvr binary 
uvr::init() 
uvr::r_install("4.5.2") 
uvr::r_pin("4.5.2")
uvr::add("rdatagouv") 
uvr::add("janitor") 
uvr::add("pheatmap")
uvr::add("pins")
uvr::add("ggplot2")

install.packages("rdatagouv")
install.packages("janitor")
install.packages("pheatmap")
library(rdatagouv)
library(janitor)
library(Factoshiny)
install.packages("pins")

library(pins)




```

```{r}
#| label: download
#| message: false
list1<-rdatagouv::dg_find_datasets(q = "climat", schema_only = TRUE) 

list1$id

dat<-rdatagouv::dg_pull_dataset("6883cd2b5196629da0088505")



#board <- board_folder("pins/", versioned = TRUE)
#df <- pin_read(board, "my-data")

```

> **Optionally pin the fetched copy** with `{pins}` so the chapter reads from a
> versioned local board instead of hitting the network on every render:
>
```{r}

board <- pins::board_folder("pins/", versioned = TRUE)
pins::pin_write(board, dat, "my-data", type = "csv")
df  <- pins::pin_read(board, "my-data")
```


## A first look and Cleaning

```{r}
#| label: skim
#| fig-cap: "A one-line summary of the dataset."
#| message: false
head(df)

df |> 
  skimr::skim() |> 
  summary()

naniar::gg_miss_var(df)

df |> tidyr::drop_na()|> head(5)

colnames(df)<-df |> clean_names() |> names()

df|> tabyl(region)

dim(df)

library(dplyr)
df<-df|>mutate(sun_hours_sum=sun_hours_q1_h+sun_hours_q2_h+sun_hours_q3_h+sun_hours_q4_h)
df<-df|>mutate(avg_temp=avg_temperature_q1_c+avg_temperature_q2_c+avg_temperature_q3_c+avg_temperature_q4_c)



colSums(is.na(df))


```





## Plotting the story



```{r}
#| label: fig-main
#| fig-cap: "The central figure of My analysis."
#| message: false


library(ggplot2)
ggplot(df, aes(x = sun_hours_sum, y = potentiel_kwh, color = region)) +
  geom_point(size = 1) +
  labs(title = "Sun hours vs Solar production potential",
       x = "Sun hours", y = "Potentiel (kWh)")+
  theme(legend.position = "bottom",    
  legend.text = element_text(size = 4),    
    legend.key.size = unit(0.3, "cm"),      
    legend.spacing.x = unit(0.1, "cm"))+
  guides(color = guide_legend(nrow = 5, byrow = TRUE)) 

ggplot(df, aes(x = avg_temp, y = potentiel_kwh, color = region)) +
  geom_point(size = 1) +
  labs(title = "average temperature vs Solar production potential",
       x = "average temperature", y = "Potentiel (kWh)")+
  theme(legend.position = "bottom",    
  legend.text = element_text(size = 4),    
    legend.key.size = unit(0.3, "cm"),      
    legend.spacing.x = unit(0.1, "cm"))+
  guides(color = guide_legend(nrow = 5, byrow = TRUE)) 


ggplot(df, aes(x = region, y = irradiation, fill = climat)) +
  geom_boxplot(notch = FALSE,
    outlier.color = "purple",
    outlier.shape = 8,
    outlier.size = 2,
    alpha = 0.7) +
  labs(title = "Irradiation distribution",
       x = "Region",
       y = "Irradiation") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 7),

    
  )


library(pheatmap)


num_df <- df[, sapply(df, is.numeric)]
num_df <- num_df[, apply(num_df, 2, function(x) sd(x, na.rm = TRUE) != 0)]
num_df<-num_df[,c(2,3,4,17,18,19,20,21,22,23,24,25)]



cor_mat <- cor(num_df, use = "pairwise.complete.obs")



pheatmap(cor_mat,
         cluster_rows = TRUE,
         cluster_cols = TRUE,
         display_numbers = TRUE,
         number_format = "%.2f",
         color = colorRampPalette(c("navy", "white", "firebrick3"))(50),
         main = "Correlation Heatmap")


```


## Findings

```{r}
#pca
sapply(df, class)

#non_char_df <- df[,!sapply(df, is.character)]
#col_variances <- sapply(non_char_df, var,na.rm=TRUE)
#dynamic_cols <-  col_variances > 0 & !is.na(col_variances)
#dfprep<-non_char_df[,dynamic_cols]
#colnames(dfprep)

#PCAshiny(dfprep)
#res.PCA<-PCA(dfprep,quali.sup=c(1,5,6,7,8,9,10,11,12,13,14,15,16),graph=FALSE)
#plot.PCA(res.PCA,choix='var')
#plot.PCA(res.PCA)

#what is the dominant factor to effect the potential of photovoltaic power generation?

colnames(df)

#climate_vars <- c("temperature_moyenne", "ensoleillement_annuel","irradiation", "sun_hours_sum","climat")
#geo_vars <- c("lat", "lon", "population","region")
#outcome_var <- "potential_kwh"  
#benefit_vars <- c("co2_evite_kg_an", "economie","roi_annees")  

pca_vars <- c("temperature_moyenne", "irradiation",
              "lat", "lon", "population")
supp_vars <- c("potentiel_kwh", "co2_evite_kg_an", "economie")

all_df <- df[, c(pca_vars, supp_vars)]
all_df <- all_df[, apply(all_df, 2, function(x) sd(x, na.rm = TRUE) != 0)]
all_df <- na.omit(all_df)


pca_res <- PCA(all_df,
               scale.unit = TRUE,
               ncp = 5,
               graph = FALSE,
               quanti.sup = which(colnames(all_df) %in% supp_vars))

summary(pca_res)
round(pca_res$quanti.sup$cor[, 1:3], 2)



```
---

*The dominant factors for photovoltaic power generation potential are temperature and irradiation. Dim.1 explains 48.2% of the variance, while temperature (loading 0.894)and radiation (loading 0.877) drives positively and the latitude (loading -0.817) drives negatively.The correlation coefficient between potentiel_kwh and Dim.1 is 0.88 which means the potentiel_kwh is determined by Dim.1. So the key point to improve potentiel_kwh is the temperature and irradation, and the region in high latitude has lower potential.*

[@wickham2019r4ds]

## References

